Computing likelihoods under the SMC for a general class of ARGs.

### 2023-12-11 paper.tex
time slice figure

\subsection{ARGs are awesome, or general intro about approximations}
% approximation: level of detail
* [Importance of ARGs: ARGs as object of theoretical reasoning vs what can be known]\\
* [difference between precision/detail and accuracy. High precision can 
give a false sense of certainty in the provided estimate].

@@

>>>>

\subsection{ARGs are awesome, or general intro about approximations}
% approximation: level of detail
%Importance of ARGs: ARGs as object of theoretical reasoning vs what can be known\\
%difference between precision/detail and accuracy. High precision can 
%give a false sense of certainty in the provided estimate].

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/3-slices.png}
\caption{Simulated ARG under Hudson coalescent (left). $N_e$ varied was constant within each of the 3 time slices: $[(0:1000): 10 000, (1000:5000): 2500, (5000:\infty):10 000]$. Remaining parameters: L=10kb, 20 diploid samples, r=2.5e-8, 148 edges in ARG). A single $N_e$ value was estimated for each slice of the ARG as defined by the true population size change time points. The inferred posterior distribution (right) using the SMC-likelihood was obtained using a uniform prior.}
 \label{fig:3-arg-slices}
\end{figure}
